---
output: github_document
title: README for icus.data
author: Alan Engel
date: January 31, 2024
lang: "en-us"
output_format: github_document
bibliography: bibliography.bib
link-citations: true
---
# icus.data

## Introduction
Between 1972 and 2000, Sun Myung Moon's organizations sponsored 22 conferences 
on the unity of science. The aim was to bring science under the moral guidance 
of Moon's organizations and their theology. The programs list 2045 participants, 
including prominent university presidents and Nobel Laureates. This project 
aims to research these conferences from multiple viewpoints.

This dataset provides several components for researchers who wish to take a deeper
look into these conferences.

## Datasets

1. __participants__ Table of 2045 people who have been
listed in ICUS programs as speakers, moderators, discussants,
advisors and other committee members

2. __programs__ Basic data for ICUS conferences from program brochures and
the ICUS website [@icushistory]

3. __role_defs__ Definitions of roles codes in __participants__

4. __whoswho__ Table of participants who are listed in Marquis
International Who's Who Editions 40, 50 and 60, which covers the first, middle
and final thirds of the ICUS conferences that ran from 1992 to 2000.

5. __nobels__ Table of Nobel Laureates who participated in ICUS conferences.

6. __icusbib__ Biblatex entries for 1658 speeches and presentations in ICUS.

## Special vignettes

1. __icus program observations__ Observations from ICUS program brochures
including, for example, attendence by Sun Myung Moon and his wife Han Hakja,
mention of funding by the Unification Church, detailed coding of program sessions
for use in Set entries in _icusbib__.

2. __build-package__ A vignette detailing the workflow for building this R data
package. I am a memory-challenged novice and this is the result of a lot of trial and error.

## Installation

You can install the latest version of __icus.data__ from [github](https://github.com/kijinosu/icus.data) with:

```{r, install-instructions, eval=FALSE}
library(devtools)
devtools::install_github("kijinosu/icus.data")
```

## Examples

### Plot participant counts by year

Load libraries.

```{r, libraries, results='hide'}
library(icus.data)
library(tidyverse)
```

Plot.

```{r, plot-participant-counts, echo=TRUE}
ggplot(data = progs) +
  geom_bar(mapping = aes(x = Year, y = Count), stat = "identity") +
  labs(title = "Participant counts by year of conference",
       x = "Year of conference")
```



### Most frequent participants

```{r, most-frequent-participants, echo=TRUE}
activeparts <- tp %>%
  count(ID, Surname, Given, Conference, name = "Roles") %>%
  count(ID, Surname, Given, name = "Conferences") %>%
  arrange(desc(Conferences)) %>%
  select(Given, Surname, Conferences) %>%
  mutate(FullName = paste(.$Given, .$Surname, sep = " ")) %>%
  select(FullName, Conferences)

knitr::kable(activeparts[1:20, ], caption = "Most frequent participants")
```

### Search on speaker

```{r, person-search}
icusbib[author = "^Oates"]
```

See [Search examples](./inst/doc/search-examples.html) for more examples.

## R packages used for this data package

* DataPackageR - Set up and put the pieces together [@R-DataPackageR]
* RefManageR - Load and process raw BibLatex files [@RefManageR2017]
and [@RefManageR2014]
* [@R-tidyverse]
* [@R-data.table]

## References
