---
title: ICUS Participants and Their Roles
author: Alan Engel
date: September 21, 2023
lang: en-us
output_format: rmarkdown::html_vignette
bibliography:
- icus.programs.bib
- kondo197808diet.bib
- R.bib
link-citations: yes
vignette: >
  %\VignetteIndexEntry{ICUS Participants and Their Roles}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## ICUS Participants and Their Roles

More than 2000 scientists and scholars participated in the 22
International Conferences on the Unity of the Sciences (ICUS)
held between 1972 and 2000. The main spreadsheet in this dataset,
\code{ICUSRoles.xlsx}, is a table of 2045 people who have been
listed in ICUS programs as speakers, moderators, discussants,
advisors and other committee members. It was manually tabulated
with emphasis on the participants roles. Other information
related with the participants is tabluated in other sheets.  

In general, the names of participants are as listed in the
ICUS programs with some modifications.  

* When participants are also found in the International Who's Who, the latter's version is used because Who's Who entries are
directly confirmed with the persons.
* When information from other sources more precisely identifies
a participant. For example, Miyajami Tatsuoki, then member of Japan's Atomic Energy Commission, is listed in the ICUS III program as "T. Miyajima." His attendence led to controversy in Japan [@kondo197808diet] that enabled more precise identification.  

In this dataset package, table \textsf{role_defs} lists definitions for single-character role codes. Table \textsf{participants} lists participants' surnames, given names,
conferences and roles, in long format. A role is only entered once even if the participant may have performed it twice or more
in a conference. This is occasionally the case for discussant (X) roles. In the spreadsheet, roles are entered as character strings with one character for each kind of role.

## R software packages used for this dataset

* readxl - To read two sheets from \code{ICUSRoles.xlsx}, which was manually prepared from the ICUS programs [@R-readxl]
* data.table - To transform the participants table to long form [@R-data.table]
* usethis - To set project folders [@R-usethis]
* DataPackageR - Set up and put the pieces together [@R-DataPackageR]

```{r libraries}
library(readxl)
library(usethis)
library(data.table)
```

## Preparation steps

The spreadsheet \code{ICUSRoles.xlsx} is locally prepared
 and is kept in a MASTER folder, where it can't be overwritten
 by \code{datapackage_skeleton}. After running \code{datapackage_skeleton} in
 R Gui or RStudio, this copied into
 \code{inst/extdata} and \code{role_defs} read directly from it.

## \code{role_defs}

 ```{r read role defs}
role_defs <- read_excel(file.path(project_path(),"inst/extdata/ICUSRoles.xlsx"),sheet="Legend")
role_defs
 ```

## \code{participants}

Four steps read and pivot \code[participants]:

1. Read sheet from file
2. Pivot on conferences columns
3. Split and transpose the strings \code{Roles}
4. Pivot on the role columns

```{r read and pivot}
pw <- as.data.table(read_excel(file.path(project_path(),"inst/extdata/ICUSRoles.xlsx"),
 sheet="CrossChart"))

## pivot to long

DT <- melt(pw, id.vars = c("ID","Surname","Given"),
            measure.vars=c("ICUS01","ICUS02","ICUS03","ICUS04","ICUS05","ICUS06",
 "ICUS07","ICUS08","ICUS09","ICUS10","ICUS11","ICUS12","ICUS13","ICUS14",
 "ICUS15","ICUS16","ICUS17","ICUS18","ICUS19","ICUS20","ICUS21","ICUS22"),
             variable.name = "Conference", 
             value.name = "Roles", na.rm=TRUE)

## tstrsplit is in data.table
## column names for up to 14 Roles
cn <- c("R1","R2","R3","R4","R5","R6","R7","R8","R9","R10","R11","R12","R13","R14")

## get max Roles string length
mr <- max(nchar(DT$Roles))

## strsplit and transpose the resulting list efficiently
DT[,cn[1:mr] := tstrsplit(Roles, "", fixed=TRUE)][]

## Drop Roles column
DT[,.SD, .SDcols = !'Roles']

## 
participants <- melt(DT[,.SD, .SDcols = !'Roles'],  
 id.vars = c("ID","Surname","Given","Conference"),
 measure.vars=cn[1:mr],
 variable.name="Temp",
 value.name="Role", na.rm=TRUE)[,.SD, .SDcols = !'Temp']
participants
```

## References

