---
title: Bibliographic dataset for ICUS programs
author: Alan Engel
date: January 22, 2024
lang: en-us
output_format: rmarkdown::html_vignette
bibliography:
- icus.programs.bib
- R.bib
link-citations: yes
vignette: >
  %\VignetteIndexEntry{Bibliographic dataset for ICUS programs}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## Bibliographic dataset for ICUS programs

__icusbib__ is a list of __RefManageR::BibEntry__ objects that covers all presentations, including
commentary, in the first 22 ICUS conferences as provided on the
ICUS website [@icushistory]. 

See [ICUS Programs: Observations and Coding](icus-program-observations.pdf) for detailed information about this dataset and its relation to the ICUS
program brochures.

## R software package used for this dataset

* RefManageR - Load and process raw BibLatex files [@RefManageR2017]
and [@RefManageR2014]

```{r libraries}
library(RefManageR)
```

## Preparation steps

__icusbib__ is compiled from manually created Biblatex files, one for each
conference. The original separate files are available in the Github repository.

## __icusbib__ 

1. Merge raw Biblatex files into a single temporary file.

2. Read temporary file into a RefManageR::BibEntry().

3. Make a vector of BibEntry keys. 

4. Each Set entry contains a __pattern__ field. 
Grep the pattern field against the vector of keys 
to get the entryset list of keys.

5. Assign the computed entryset lists to their respective
Set entries.

```{r icus_icusbib, echo=TRUE, error=TRUE}
srcpath <- file.path(project_path(), "inst/extdata/icusbib-raw")
files <- list.files(path = srcpath, pattern = "icus[0-9][0-9].bib",
                    full.names = TRUE, recursive = FALSE)

tmpbib <- tempfile("icus", fileext = ".bib")
file.create(tmpbib)

btmp <- RefManageR::BibEntry()

lapply(files, function(x) {
  file.append(tmpbib, x)
})

btmp <- RefManageR::ReadBib(tmpbib)
k <- unlist(btmp$key)
ps <- btmp[btmp$bibtype == "Set", ]$pattern
len <- length(ps)
es <- sapply(1:len, function(i) {
  ms <- k[grep(ps[i], k)]
  paste0(ms, collapse = ",")
})
e1 <- parent.frame()
esetout <- eval(es, e1)

btmp[btmp$bibtype == "Set",]$entryset <- esetout

icusbib <- btmp
icusbib
```

## References

