---
title: Searching the __bibset__ dataset
author: Alan Engel
date: January 25, 2024
lang: en-us
output_format: rmarkdown::html_vignette
bibliography: simple-examples.bib
link-citations: yes
vignette: >
  %\VignetteIndexEntry{Searching the __bibset__ dataset}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Searching the ```bibset``` dataset

```bibset``` is a list of ```RefManageR::BibEntry``` objects that covers all presentations, including
commentary, in the first 22 ICUS conferences as provided on the
ICUS website [@icushistory]. 

This vignette will illustrate various searches.

# The underlying RefManageR package

This package is built on Mathew McLean's ```RefManageR``` package[@refmanager], which in turn
builds on \emph{Bibtex}[@bibtex] and \emph{BibLatex}[@biblatex]. In presenting the examples
below, I will try to remain consistent with these references.

Begin by loading the required R libraries.

```{r, load-libraries, results='hide'}
library(RefManageR)
library(icus.data)
```

# Structure and output styles

Let's take a look at the first entry in ```bibset```.

```{r, first-look}
bibset[1]
```

RefMangeR's default output style is "numeric".

```{r, default-style}
BibOptions("bib.style")
```
To see the Biblatex entry in full, we use the ```toBiblatex()``` function.

```{r, toBiblatex-1}
toBiblatex(bibset[1])
```
The original bibliographic file ```ICUS01.bib``` contained the following.
```
@Proceedings{ICUS01,
title={Moral Orientation of the Sciences},
titleaddon={First International Conference on Unified Science},
shorttitle={ICUS I},
eventdate={1972-11-23/1972-11-26},
venue={Waldorf-Astoria Hotel},
organization={Council for Unified Research and Education},
location={New York, New York},
date={1972},
url ={https://icus.org/wp-content/uploads/2016/03/1st-ICUS-New-York-City-1972.pdf},
urldate={2023-05-01},
keywords={primary, program, moonist}
}
```

__bibset__ uses the three entry types ```@Proceedings```, ```@InProceedings``` and ```@Set```. 
__icus.date__ uses the __key__ field to capture the hierarchy, tracks and sessions of ICUS
conferences. For details, please see [ICUS Programs: Observations and Coding](https://osf.io/c2nd6
"ICUS Programs: Observations and Coding"). In this record, 'ICUS01' stands for the main entry
for ICUS I. 

The first entry in __bibset__ is a ```@Proceedings``` entry. Now take a look at an ```@InProceedings```
entry from the same conference. This is the entry in the manually prepared bibliographic files.
You can view this file [here](https://osf.io/ksr2q).

```
@InProceedings{ICUS01:C01:G01:S01,
crossref={ICUS01},
author={Camilo Dagum},
title={The Impact of Unified Science on Economics}
}
```
```toBiblatex()``` outputs the following. This shows that RefManageR folds the content of ```bibset[1]```
into this entry based on the value of ```crossref```. Searches are on these combined entries. It should
be evident that changing keys will corrupt the dataset.
```{r, toBiblatex-4}
toBiblatex(bibset[4])
```
Possible values for ```bib.style``` are “numeric” (default), “authoryear”, “authortitle”, “alphabetic”,
“draft”. (See [RefManageR on CRAN](https://cran.r-project.org/web/packages/RefManageR/RefManageR.pdf) for
details.) These styles are illustrated below.
```{r, style-examples}
bibset[4]
oldstyle <- BibOptions(bib.style = "authoryear")
bibset[4]
BibOptions(bib.style = "authortitle")
bibset[4]
BibOptions(bib.style = "alphabetic")
bibset[4]
BibOptions(bib.style = "draft")
bibset[4]
BibOptions(oldstyle)
```
The bibliographic style can also be selected in ```print``` so that you do not to change
the global option just for one output.
```{r, print-style}
print(bibset[4], .opts = list(bib.style = "draft"))
```
Now let's take a look at the structure of this BibEntry.
```{r, structure}
str(bibset[4])
```

# References


