---
title: ICUS participants listed in the International Who's Who and Nobel Laureates
author: Alan Engel
date: September 21, 2023
lang: "en-us"
output_format: rmarkdown::html_vignette
bibliography: 
  - gsheets.bib
  - R.bib
link-citations: true
---
```{r libraries}
library(dplyr)
library(googlesheets4)
library(data.table)
```

This script downloads tables from Google Sheets. Putting multiple downloads in
one Rmd file reduces to one the number of times one has to enter a Google ID.

Tables in script:

* whoswho
* nobels

## whoswho

The main table in this dataset, \code{participants}, is a list of 2045 people
who have been listed in ICUS programs as speakers, moderators, discussants,
advisors and other committee members. For the purpose of assessing the roles
of Nobel Laureates and other famous persons, the full list was looked up
in three editions of Marquis International Who's Who Editions 40 [@intlwhoswho1976],
50 [@intlwhoswho1986] and 60 [@intlwhoswho1996]. This data is in the 
\code{whoswho.rda} file.

These editions cover the first, middle and final thirds of the ICUS
conferences that ran from 1992 to 2000. 

For ease of handling during manual lookups, the origional datasheets were
compiled as Google Sheets, which can be easily accessed via phone. These
wide tables are included with the dataset in the \code{inst/extdata} folder.

The table \code{whoswho} itself is in long form in the \code{whoswho.rda} file.

## Fetch icus who's who data from Google sheets

```{r whoswho}
gm <- readline(prompt = "Google account: ")
gs4_auth(scopes = "spreadsheets.readonly", email=gm) 
ss <- "https://docs.google.com/spreadsheets/d/1l8y_tp55rojn73308TTLr2yq_nZaeJC5v6CnKrZvS0s/edit?usp=sharing"
ww <- read_sheet(ss,sheet="Intl Who’s Who", na="N", trim_ws=TRUE)
ww1 <- as.data.table(ww)
write.csv(ww,file=file.path(project_path(),"inst","extdata","whoswho.csv"),fileEncoding="utf8")
write.table(ww1, file = file.path(project_path(),"inst","extdata","whoswho.tsv"), row.names=FALSE, sep="\t")
whoswho <- melt(ww1, id.vars = c("ID","Surname","Given"),
            measure.vars=c("IntlWW40","IntlWW50","IntlWW60"),
             variable.name = "Edition", 
             value.name = "Birthdate", na.rm=TRUE)
whoswho
```

## nobels

In his 1977 criticism of ICUS IV, Irving Horowitz noted the prominence of Nobel
Laureates on the program and a striking fall-off in talent beyond a stellar list of
sponsors [@horowitz1977science]. This table is based on the Nobel Media AB
dataset [@nobelprizelaureates2023].

The categories are:

* C - Chemistry
* E - Economics
* M - Medicine and physiology
* P - Physics
* S - Peace

```{r nobels}
ss <- "https://docs.google.com/spreadsheets/d/1f09qZiFsVZVLnoSUMfkGqw7cpk1Y4OG9OvW3qnSVSwE/edit?usp=sharing"
nobels <- as.data.table(read_sheet(ss,sheet="Nobels", na="N",trim_ws=TRUE))[Year > 1800]
nobels
```

## References
