---
title: ICUS Program Brochures
author: Alan Engel
date: September 26, 2023
lang: "en-us"
output_format: rmarkdown::html_vignette
bibliography: 
  - icus.programs.bib
  - R.bib
link-citations: true
---

## ICUS Programs

Basic data for ICUS conferences came from programs brochures and
the ICUS website [@icushistory]. This includes year, location,
country, program title, number of participants and the number of
nations they represent. This basic data also includes the number of
pages in the brochures and coding for the pages based on their type
of content. Compiling this coding was prompted by an observation that
programs in the latter half of this series contained almost as many
pages of promotional material for the sponsor as pages listing the
schedule of speakers. Please see the vignette "Observations about
ICUS program brochures for a description of this coding scheme and
qualitative observations about the program brochures.

## \code{ICUSPrograms.xlsx}

A copy of the Excel spreadsheets used in compiling program brochure data,
\code{ICUSPrograms.xlsx}, is in folder \code{extdata}. It contains a
\code{Summary} sheet and one sheet for each conference. Each conference
sheet consists of a column \code{Page} of page numbers (per the PDF file
of the program, not
the page number in the brochure), the \code{Coding} (or category) assigned by me
to the page, and \code{Remarks}.

The \code{Summary} sheet contains columns for each of the codes (categories)
that tally the number of pages for the respective categories. The
\code{data.table} \code{programs} is from the \code{Summary} sheet.
The documentation for \code{programs} contains an example of fetching a
conference sheet from \code{ICUSPrograms.xlsx} for researchers who may
want to work directly with them.

For researchers who wish to view the brochures themselves, please see the links below.

* ICUS I [@ICUS01Program]
* ICUS II [@ICUS02Program]
* ICUS III [@ICUS03Program]
* ICUS IV [@ICUS04Program]
* ICUS V [@ICUS05Program]
* ICUS VI [@ICUS06Program]
* ICUS VII [@ICUS07Program]
* ICUS VIII [@ICUS08Program]
* ICUS IX [@ICUS09Program]
* ICUS X [@ICUS10Program]
* ICUS XI [@ICUS11Program]
* ICUS XII [@ICUS12Program]
* ICUS XIII [@ICUS13Program]
* ICUS XIV [@ICUS14Program]
* ICUS XV [@ICUS15Program]
* ICUS XVI [@ICUS16Program]
* ICUS XVII [@ICUS17Program]
* ICUS XVIII [@ICUS18Program]
* ICUS XIX [@ICUS19Program]
* ICUS XX [@ICUS20Program]
* ICUS XXI [@ICUS21Program]
* ICUS XXII [@ICUS22Program]

## Reading in \code{programs}

First load the libraries.

```{r libraries}
library(readxl)
library(usethis)
library(data.table)
```

Then read the \code{Summary} sheet directly into
\code{programs}.

```{r read sheet}
## Sheet 'Summary' is partly aggregated from sheets that were compiled for
## each conference.
programs <- as.data.table(read_excel(file.path(project_path(),"inst/extdata/ICUSPrograms.xlsx"),
sheet="Summary"))
```

## Look at a couple columns

```{r look}
programs$ProgTitle
programs$Structure
```

## R software packages used for this dataset

* readxl - To read two sheets from
\code{ICUSPrograms.xlsx}, which was manually prepared
from the ICUS programs [@R-readxl]
* data.table - [@R-data.table]
* usethis - To set project folders [@R-usethis]
* DataPackageR - Set up and put the pieces together [@R-DataPackageR]

## References
